Papers

### 2023-02-24 quarto/index.qmd
update

---
about:
  id: az-heading
  template: trestles
  image: img/aston.jpg
  image-width: 200px
  image-shape: rounded
  links:
    - icon: twitter
      text: Twitter
      href: https://twitter.com/astonzhangAZ
    - icon: file-earmark-person-fill
      text: Email
      href: img/email.png
    - icon: github
      text: GitHub
      href: https://github.com/astonzhang
---

>>>>

---
about:
  id: az-heading
  template: trestles
  image: img/aston.jpg
  image-width: 200px
  image-shape: rounded
  links:
    - icon: twitter
      text: Twitter
      href: https://twitter.com/astonzhangAZ
    - icon: file-earmark-person-fill
      text: CV
      href: https://www.dropbox.com/s/ey71hf621x7duho/CV-Aston.pdf?dl=0
    - icon: github
      text: GitHub
      href: https://github.com/astonzhang
---
